figures_manuscript

### 2025-07-17 1_data_processing/1_data_processing.Rmd
Rstudio fix
manuscript figures, new structure, PCA, Counts, Voclanos
interaction counts pdf

# gene_name info sind in gff3 abder nicht in se?
coldata_Cre <- filter(coldata, species == "Cre")
se <- tximeta(coldata_Cre, useHub=T)
se

@@

@@

>>>>

# gene_name info sind in gff3 abder nicht in se?
coldata_Cre <- filter(coldata, species == "Cre")
se <- tximeta(coldata_Cre, useHub=F)
se

@@

colnames(anno)

@@

anno_xls <- subset(anno, select = -previousIdentifiers_list)
write_xlsx(data.frame(anno_xls),
           paste(gitdir,"Chlamy_master_annotation.xlsx",sep="/"))

### 2025-07-17 pub_figures/manuscript-figures_bu.Rmd
interaction counts pdf

# Fig. X
```{r 3_groups, eval=FALSE, fig.show='hold', fig.width=6, fig.height=4, dpi=300, out.width="50%"}

>>>>

# Fig. 5: pCRY interaction partner
## load csv
```{r load_interaction}
top20 <- read.csv2("../UniProt-and-Cre-ID's.csv")
top20_id <- top20$'Cre.ID' %>% str_remove_all(pattern=" ")
summary(top20_id %in% anno$gene_id)

## Plot interaction counts
```{r plot_interaction}
## Interaction genes all-in-one
fig <- "Fig5"
goi_interaction <- top20_id
anno_interaction <- anno[top20_id,]

goi <- anno_interaction
l <- nrow(goi)
all_counts <- {}
for (i in 1:l){
  d <-  plotCounts(dds, gene=goi[i,"gene_id"], intgroup=c("condition","experiment","treatment","genotype"), col=col,main=res$SYMBOL[i],returnData=TRUE)
  d$Gene <- rep(goi[i,"id.symbol"],length(rownames(d)))
  d$sample <- rownames(d)
  rownames(d) <- {}
  all_counts <- bind_rows(all_counts,d)
  }

all_counts$Gene <- factor(all_counts$Gene)
all_counts$Gene <- fct_reorder(all_counts$Gene, all_counts$count, .fun = median, .desc = TRUE)
levels(all_counts$Gene)

# all_counts$Gene <- factor(all_counts$Gene, levels = c("PHOT1","CHR1","CHR2","HKR1","UVR8","DCRY1","PCRY1","ACRY1")) # "DCRY2", 
# levels(all_counts$Gene)

# Plot
max_val <- 1.0*max(all_counts$count)
gcounts_interaction <- ggplot(all_counts, aes(x = Gene, y = count, fill=condition)) +
  geom_boxplot(fatten = 1) +
  scale_fill_manual(values = group.colors) +
  labs(title = "Interaction partners") + 
  theme_bw() +
  removeGrid(x=T, y=T) +
  geom_vline(xintercept=seq(1,length(levels(all_counts$Gene))-1,1)+.5,color="grey") +
  scale_y_continuous(trans = "log2") & plot_annotation(title = colData(dds)$experiment[1])
gcounts_interaction %>% print()

ggsave(paste(fig,"_",colData(dds)$experiment[1],"_Counts_Interaction.pdf",sep=""), plot = gcounts_interaction,
width = 30,
height = 8)

# Fig. Y
```{r 3_groups, eval=FALSE, fig.show='hold', fig.width=6, fig.height=4, dpi=300, out.width="50%"}
